Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-06-02 fib2.tex
Changed equation.
added (very rough) potential sequence of fusion diagrams to explain figure 2.

These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees. For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
\begin{align}
	R_{\mathbb{I}}^{\tau\tau}&= \e^{\frac{-4\pi i}{5}}\qquad R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}}\\
	F_{\tau}^{\tau\tau\tau} &= \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
\end{align}
where the matrix is given in a basis labelled $(\mathbb{I},\tau)$.

@@

In \Fref{f:syndrome} we show two adjacent sites
involved in a syndrome measurement.
%This will be the total charge on each site, ie. either $\tau$ or $\mathbb{I}.$
The error process has resulted in two pair
creation events along the edge joining these sites.
\dude{i'd like to write out the equations for each of
these 4 steps, but we'd need to keep it tight somehow.}
First, (a) we show the state as a tensor product of two pairs $\tau\tau\otimes\tau\tau$.
Then, (b) these two pairs are embedded into a single larger fusion
tree $\tau\tau\tau\tau$.
This is continuously deformable into the picture in (c).
It is now clear the two braid operations required so
that the observables are represented on the fusion tree.
The general algorithm and data structures used
for this procedure will be discussed elsewhere.

>>>>

These manipulations encode the data of the unitary modular tensor category, and can be used to represent the state of a system of anyons as a linear combination of fusion trees. For the Fibonacci anyons, the non-trivial $R$ and $F$ moves are given by
\begin{equation*}
	R_{\mathbb{I}}^{\tau\tau} = \e^{\frac{-4\pi i}{5}} 
	\ \ , \ \
	R_\tau^{\tau\tau}= \e^{\frac{3\pi i}{5}} 
	\ \ , \ \
	F_{\tau}^{\tau\tau\tau} = \begin{pmatrix}\varphi^{-1}&\varphi^{-\frac{1}{2}}\\\varphi^{-\frac{1}{2}}&-\varphi^{-1}\end{pmatrix} \,,
\end{equation*}
where the matrix is given in a basis labelled $(\mathbb{I},\tau)$.

@@

In \Fref{f:syndrome} we show two adjacent sites
involved in a syndrome measurement.
%This will be the total charge on each site, ie. either $\tau$ or $\mathbb{I}.$
The error process has resulted in two pair
creation events along the edge joining these sites.
\dude{i'd like to write out the equations for each of
these 4 steps, but we'd need to keep it tight somehow.}

\newcommand{\verteq}{\rotatebox{90}{$\,=$}}
\begin{align*}
		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
			\draw(1,0)--(0,1)[dashed];
			\draw(0,1)--(-1,2)--(-1,3);
			\draw(0,1)--(1,2)--(1,3);
			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
			\node at (1,3) [anchor=west] {{\scriptsize $2$}};
			%			
			\begin{scope}[xshift=4cm]
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(-1,3);
				\draw(0,1)--(1,2)--(1,3);
				\node at (-1,3) [anchor=west] {{\scriptsize $3$}};
				\node at (1,3) [anchor=west] {{\scriptsize $4$}};
			\end{scope}
		\end{tikzpicture}\\
		&\qquad\;\downarrow\\
		&\begin{tikzpicture}[baseline=0.5cm,scale=0.3]
			\begin{scope}[xshift=2cm,yshift=2cm]		
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(-1,3);
				\draw(0,1)--(1,2)--(1,3);
				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
			\end{scope}
			%			
			\begin{scope}[xshift=4cm]
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(1,4)--(1,5);
				\draw(0,1)--(3,4)--(3,5);
				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
			\end{scope}
		\end{tikzpicture}\\
		&\qquad\downarrow\\
		&\begin{tikzpicture}[baseline=1.5cm,scale=0.3]
			\begin{scope}[xshift=2cm,yshift=2cm]		
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(-1,7);
				\draw(0,1)--(1,2)--(1,5);
				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
				\node at (1,3) [anchor=west] {{\scriptsize $2$}};
				\node at (-1,7) [anchor=west] {{\scriptsize $1$}};
				\node at (1,7) [anchor=west] {{\scriptsize $4$}};
			\end{scope}
			%			
			\begin{scope}[xshift=4cm]
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(1,4)--(1,5);
				\draw(0,1)--(3,4)--(3,5);
				\draw(3,7)--(3,9);
				\node at (1,5) [anchor=west] {{\scriptsize $3$}};
				\node at (3,5) [anchor=west] {{\scriptsize $4$}};
				\node at (1,9) [anchor=west] {{\scriptsize $2$}};
				\node at (3,9) [anchor=west] {{\scriptsize $3$}};
			\end{scope}
			%
			\begin{scope}[xshift=6cm,yshift=2cm]
				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
			\end{scope}
			\begin{scope}[xshift=4cm,yshift=4cm]
				\draw plot [smooth, tension=1] coordinates { (1,3) (0.75,3.8) (-0.6,4.45) (-1,5)};
				\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
				\draw plot [smooth, tension=1] coordinates { (-1,3) (-0.75,3.8) (0.6,4.45) (1,5)};
			\end{scope}
		\end{tikzpicture}\\
		&\qquad\verteq\\
		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
		&\begin{tikzpicture}[baseline=0.8cm,scale=0.3]
			\begin{scope}[xshift=2cm,yshift=2cm]		
				\draw(1,0)--(0,1)[dotted];
				\draw(0,1)--(-1,2)--(-1,3);
				\draw(0,1)--(1,2)--(1,3);
				\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
				\node at (1,3) [anchor=west] {{\scriptsize $4$}};
				\node at (0.7,0.2) [anchor=east] {{\scriptsize $j'$}};
			\end{scope}
			%			
			\begin{scope}[xshift=4cm]
				\draw(1,0)--(0,1)[dashed];
				\draw(0,1)--(-1,2)--(1,4)--(1,5);
				\draw(0,1)--(3,4)--(3,5);
				\node at (1,5) [anchor=west] {{\scriptsize $2$}};
				\node at (3,5) [anchor=west] {{\scriptsize $3$}};
			\end{scope}
		\end{tikzpicture}\\
		&\qquad\verteq\\
		\sum_{j,j'\in\{\mathbb{I},\tau\}}R^{\tau\tau}_{\mathbb{I}}[F^{\tau\tau\tau}_{\tau}]_{\mathbb{I}j}R^{\tau\tau}_{j}[F^{\tau\tau\tau}_{\tau}]^{-1}_{jj'}\;\;
		&\begin{tikzpicture}[baseline=0.2cm,scale=0.3]		
			\draw(2,-1)--(0,1)[dotted];
			\draw(0,1)--(-1,2)--(-1,3);
			\draw(0,1)--(1,2)--(1,3);
			\node at (-1,3) [anchor=west] {{\scriptsize $1$}};
			\node at (1,3) [anchor=west] {{\scriptsize $4$}};
			\node at (1,0) [anchor=east] {{\scriptsize $j'$}};
			\draw(2,-1)--(2,-2)[dashed];
			%			
			\begin{scope}[xshift=4cm]
				\draw(-2,-1)--(0,1)[dotted];
				\draw(0,1)--(-1,2)--(-1,3);
				\draw(0,1)--(1,2)--(1,3);
				\node at (-1,3) [anchor=west] {{\scriptsize $2$}};
				\node at (1,3) [anchor=west] {{\scriptsize $3$}};
				\node at (-1,0) [anchor=west] {{\scriptsize $\bar{j'}$}};
			\end{scope}
		\end{tikzpicture}
\end{align*}
\cggb{Here 1,2,3,4 are meant to refer to the 4 different leaves in \Fref{f:syndrome} a) taken clockwise from the top left (equivalently those in c) taken down the page). The first diagram represents a), the second b) and c) together, and the last three d). Is this correct? Of course I would clean and explain these properly if this is the kind of thing we want. Also I haven't been very careful with the calculation. I would need to check if there is a Frobenius-Schur indicator missing on the last line. We could also do something like make circles above 1,4 and 2,3 at the end to show the measurements being made in the figure or something.}

	\begin{align}
		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
			\draw(0,0)--(0,1);
			\draw plot [smooth, tension=1] coordinates { (0,1) (0.75,1.8) (-0.6,2.45) (-1,3)};
			\draw[color=white, line width=7] plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
			\draw plot [smooth, tension=1] coordinates { (0,1) (-0.75,1.8) (0.6,2.45) (1,3)};
			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
		\end{tikzpicture}
		&\;\;=\;\;R^{ab}_c\cdot\;
		\begin{tikzpicture}[baseline=0.5cm,scale=0.3]		
			\draw(0,0)--(0,1);
			\draw(0,1)--(-1,2)--(-1,3);
			\draw(0,1)--(1,2)--(1,3);
			\node at (0,0) [anchor=west] {{\scriptsize $c$}};
			\node at (-1,3) [anchor=east] {{\scriptsize $b$}};
			\node at (1,3) [anchor=west] {{\scriptsize $a$}};
		\end{tikzpicture}
	\end{align}
where $a$, $b$, and $c$ represent particle types, or $F$-moves, representing the associativity rule for fusion processes, denoted as
	\begin{align}
		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]
			\draw(0,0)--(0,1)--(-2,3);
			\draw(0,3)--(-1,2);
			\draw(2,3)--(0,1);
			\node at (-0.45,1.6) [anchor=north east] {{\scriptsize $i$}};
			\node at (0,0) [anchor=west] {{\scriptsize $d$}};
			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
		\end{tikzpicture}
		&\;\;=\;\;\sum_j[F^{abc}_d]_{ij}\cdot\;
		\begin{tikzpicture}[baseline=0.6cm,scale=0.3]		
			\draw(0,0)--(0,1)--(-2,3);
			\draw(0,3)--(1,2);
			\draw(2,3)--(0,1);
			\node at (0.42,1.63) [anchor=north west] {{\scriptsize $j$}};
			\node at (0,0) [anchor=east] {{\scriptsize $d$}};
			\node at (2,3) [anchor=east] {{\scriptsize $c$}};
			\node at (0,3) [anchor=east] {{\scriptsize $b$}};
			\node at (-2,3) [anchor=east] {{\scriptsize $a$}};
		\end{tikzpicture}
	\end{align}

First, (a) we show the state as a tensor product of two pairs $\tau\tau\otimes\tau\tau$.
Then, (b) these two pairs are embedded into a single larger fusion
tree $\tau\tau\tau\tau$.
This is continuously deformable into the picture in (c).
It is now clear the two braid operations required so
that the observables are represented on the fusion tree.
The general algorithm and data structures used
for this procedure will be discussed elsewhere.
